---
title: "FARS Package Overview"
author: "Jerad Tintera"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,eval = FALSE)
```

## Fatality Analysis Reporting System (FARS)

This is a document higlighting the functionality of the FARS package. The functions included with this package allow you to summarize data from FARS and plot accident data on a map.

## Summarizing data

You can use **fars_summarize_years** to summarize accident data for a selection of years. The function takes a vector of years and returns a dataframe with the number of accidents summarized by year and month.

```{r}
fars_summary <- fars_summarize_years(c('2013','2014','2015'))
```

## Plotting accidents on a map

You can use **fars_map_state** to plot accident data for a specific state and year on a map. The function takes a state code and year and plots accident locations on a map.

```{r}
fars_map_state(23,'2015')
```
